---
title: ggrough a good way make graphics look user generated
author: Michael DeWitt
date: '2018-07-05'
slug: ggrough-a-good-way-make-graphics-look-user-generated
categories:
  - dataviz
  - ggplot2
tags:
  - dataviz
  - ggplot2
---

So I came across another `ggplot2` package which I like. It bootstraps off of a javascript library called `roughjs`. I like that you can make graphs and charts that look handdrawn. This is a great feature when doing data communication. It makes the look less clinical which might be a good tactic when doing a data visualisation clinic where the focus is on the chart type and how it communicates.

Warm and friendly is a good approach when doing these types of trainings with graphical neophytes.

The package information is [here](https://xvrdm.github.io/ggrough/)


Some examples of their code are below:

```{r}
library(tidyverse)
library(ggrough)
```

```{r}
count(mtcars, carb) %>%
  ggplot(aes(carb, n)) +
  geom_col() + 
  labs(title="Number of cars by carburator count") + 
  theme_grey(base_size = 16) -> p 
p
```

```{r}
options <- list(
  Background=list(roughness=8),
  GeomCol=list(fill_style="zigzag", angle_noise=0.5, fill_weight=2))
get_rough_chart(p, options)
```


