---
title: Exploring forecast
author: Michael DeWitt
date: '2018-07-08'
slug: exploring-forecast
categories:
  - timeseries
  - forecasting
  - r
tags:
  - timeseries
  - r
  - forecasting
---

Time series forecasting is interesting. I want to write more,  but not right now. I'm just going to lay out a few functions for explanation later.

```{r}
library(fpp2)
library(purrr)
library(dplyr)
```

I am going to test a few different methods:

* Mean forecasting

* Random Walk (last value is forecast with an addition)

* Seasonal Naive (last seasons value is next guess)

* Naive (Previous value is forecast)

```{r}
beer2 <- window(ausbeer, start= 1992, end = c(2007,4))

beer_fit1 <- meanf(beer2, h=10)
beer_fit2 <- rwf(beer2, h=10)
beer_fit3 <- snaive(beer2, h=10)
beer_fit4 <- naive(beer2, h=10)
```


Let's see how we did on the forecast.

```{r}
beer3 <- window(ausbeer, start =2008)

models <- list(mean_forecast = beer_fit1, rand_walk = beer_fit2, seasonal_naive = beer_fit3,
               naive = beer_fit4)
map(models, accuracy, beer3)

```

